Finally, functional class scoring enrichment analysis of Infinium DNA methylation data

### 2023-11-01 manuscript/manuscript.Rmd
ms

>>>>

Simulations were conducted using the seven FCS methods (LAT, LTT, LAW, LAM, ALT, ALW, ALM) and GSAmeth,
with group sizes of 3-12 and delta values between 0.1 and 0.5, and random gene sets with sizes 20, 50
and 100.
Precision and recall were calculated for these tests (Figure 1).
As expected, precision and recall values were better when group sizes and delta values were larger.

These data showed a strong relationship between the size of the gene sets and the precision and recall,
regardless of the enrichment test used.
On the whole, precision and recall were better
